Formalization of Forcing in Isabelle/ZF

### 2020-11-30 src/document/root.tex
Fixed latex compilation

\documentclass[11pt,a4paper]{article}
\usepackage{isabelle,isabellesym}
\usepackage[numbers]{natbib}

@@

\title{Formalization of Forcing in Isabelle/ZF}
\author{Emmanuel Gunther
  \and
  Miguel Pagano
  \and
  Pedro S\'anchez Terraf
}
\maketitle

@@

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{isabelle,isabellesym}
\usepackage[numbers]{natbib}
\usepackage{babel}

@@

\title{Formalization of Forcing in Isabelle/ZF}
\author{Emmanuel Gunther\thanks{Universidad Nacional de C\'ordoba. 
    Facultad de Matem\'atica, Astronom\'{\i}a,  F\'{\i}sica y
    Computaci\'on.}
  \and
  Miguel Pagano\footnotemark[1]
  \and
  Pedro S\'anchez Terraf\footnotemark[1] \thanks{Centro de Investigaci\'on y Estudios de Matem\'atica
    (CIEM-FaMAF), Conicet. C\'ordoba. Argentina.
    Supported by Secyt-UNC project 33620180100465CB.}
}
\maketitle

@@

A cross-linked HTML version of the development can be found at
\url{https://cs.famaf.unc.edu.ar/~pedro/forcing/}.
